More than one Author with different Affiliations

### 2012-04-22 paper/ms.tex
Tidied up some stuff

The prior probability distribution for the unknown parameters can be factorised
using the product rule. In its most general form, this is:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha|N)p(\beta|\alpha,N)\prod_{i=1}^N 
\end{eqnarray}
However, we make a variety of independence assumptions, which simplifies the
prior
distribution to:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha)p(\beta)\prod_{i=1}^N p(x_i, y_i | \alpha)
p(f_i | \beta) 
\end{eqnarray}

Here, we have assumed that the luminosity function does not depend on position.

In summary, the unknown parameters are $\{(x_i, y_i, f_i)\}_{i=1}^n$
and $\alpha$.

\section{A Toy Model}

\begin{eqnarray}
N &\sim& \textnormal{Uniform}(0, 1, 2, ..., 1000) \\
\alpha &=& \left\{x_c, y_c, \sigma\right\} \\
\end{eqnarray}

\begin{table}
\begin{tabular}{ccc}
Parameter & \vline & Prior \\
\hline \\
N & & \\
\end{tabular}
\end{table}

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image
gives rise to the observed data. First, it is convolved with a
PSF $g(x,y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x,y) &=& \iint f(x, y)g(x - \delta_x, y - \delta_y)
\, d\delta_x \, d\delta_y
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation, such that
the flux within a pixel is:
\begin{eqnarray}
F &=& \iint_{\rm{pixel}} f_{\rm blurred}(x, y) \,dx\,dy
\end{eqnarray}

>>>>

The prior probability distribution for the unknown parameters can be factorised
using the product rule. With a variety of independence assumptions, the prior
can be written as:
\begin{eqnarray}
p(\theta) = p(N)p(\alpha)p(\beta)\prod_{i=1}^N p(x_i, y_i | \alpha)
p(f_i | \beta) 
\end{eqnarray}

Here, we have assumed that the luminosity function does not depend on position.
We have also assumed independence of $N$, $\alpha$ and $\beta$, which means that
learning the value of one would not tell us anything about the values of the
others. Finally, the positions and fluxes of the stars come independently from
a common distribution. If we knew the spatial distribution and the luminosity
function of the stars, then the location and flux of a particular star would not
tell us anything about the location and flux of another star.

\section{Particular Models}
A model for the spatial distribution corresponds to a choice of functional forms
for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(x, y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x, y)g(x - \delta_x, y - \delta_y)
\, d\delta_x \, d\delta_y
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation, such that
the true flux $F$ within a particular pixel is:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} f_{\rm blurred}(x, y) \,dx\,dy
\end{eqnarray}
